Efficient Compilation of High Level Python Numerical Programs with Pythran

### 2014-09-04 doc/papers/cgo2014/paper.tex
Update table result
* Parakeet perform really well on julia...

    \centering{
\begin{tabular}{|l||c|c|c|c|c|}
\hline
& Python & numba & parakeet & pypy & pythran \\
\hline
\hline
       allpairs\_distances &   37727 &             0 &          1768 &         36855 & \textbf{1079} \\
allpairs\_distances\_loops &   49799 &         55867 &          1781 &         50253 & \textbf{1758} \\
             arc\_distance &    1365 &          1401 &          1596 &          1364 &  \textbf{494} \\
                      conv & 1926454 &       2356675 &          2032 &       1899006 & \textbf{1944} \\
              create\_grid &    3867 &          3950 &             0 & \textbf{3833} &          5512 \\
                  cronbach &    1637 &          1681 &             0 &          1756 & \textbf{1136} \\
                 diffusion &   22511 &         23564 &         21167 &         22450 & \textbf{9606} \\
                    evolve &    5762 &             0 &             0 &          5522 & \textbf{3841} \\
                      fdtd & 1558799 &       1824395 &             0 &       1538692 & \textbf{1198} \\
                       fft &   25720 &             0 &             0 &         24771 & \textbf{1211} \\
                  grouping &    2095 &             0 &             0 &          2104 &  \textbf{839} \\
                   growcut & 1807849 &          5573 & \textbf{2200} &       1860926 &          3930 \\
                    harris &    5516 &          5258 &          5084 &          5500 & \textbf{2994} \\
                   hyantes &  259268 &             0 & \textbf{1865} &        261074 &          2359 \\
                     julia & 2716770 &          2716 &          2930 &       2776183 & \textbf{2636} \\
                    l2norm &    6057 &          6008 &         12574 &          6069 &  \textbf{540} \\
             local\_maxima &   59822 &             0 &             0 &         60504 & \textbf{5084} \\
                    lstsqr &    7886 &          8652 &             0 &          7891 & \textbf{1680} \\
                    mandel &  437908 & \textbf{4361} &             0 &        439827 &          5075 \\
             multiple\_sum &    2981 &          3194 &          8206 &          2975 & \textbf{2007} \\
                  pairwise & 3888235 &          5777 &          3699 &       3873927 & \textbf{3435} \\
            periodic\_dist &    1848 &          1983 &             0 &          1863 &  \textbf{951} \\
                 repeating &    1216 &          1228 &             0 &          1226 &  \textbf{568} \\
           reverse\_cumsum &    2620 &          2629 &             0 &          2614 & \textbf{2389} \\
                     rosen &   14693 &         19419 &          1557 &         14611 &  \textbf{894} \\
                 slowparts &    5687 &             0 & \textbf{1223} &          5900 &          1537 \\
                 smoothing &  911126 & \textbf{4858} &          6258 &        935202 &          4924 \\
           specialconvolve &    8211 &          6665 &         10340 &          8140 & \textbf{2449} \\
              vibr\_energy &    2563 &          2450 &          2488 &          2548 & \textbf{1112} \\
                      wave &   54234 &         54529 &             0 &         51471 & \textbf{1886} \\
                     wdist &   82669 &         90274 & \textbf{1457} &         80406 &          1469 \\
\hline
\end{tabular}
}
\caption{Average execution times for all kernels of the numpy-benchamrks.}
\label{tbl:overview}
\end{table*}

Figure~\ref{fig:arc_distance} and \ref{fig:arc_distance_intel8} are typicals
example where we can make intensive
use of the techniques described in this paper. It measures performances on the
arc\_distance benchmark. It is a kernel with intensive points to points computation
and trigonometrics use. As we can see, both vectorization
and parallelization have an impact on execution time. We can notice that SIMD
contribution is not as good on AMD48 as it is on Intel8, because it does not
support AVX. This program also benefits from OpenMP and is scalable up to 20 cores.
The input is a raw array of 10,000,000 double elements.

>>>>

    \centering{
\begin{tabular}{|l||c|c|c|c|c|}
\hline
& Python & numba & parakeet & pypy & pythran \\
\hline
\hline
         allpairs\_distances &   58293 &             0 &          3170 &   59232 & \textbf{1583} \\
  allpairs\_distances\_loops &   64137 &         72748 &          3158 &   65287 & \textbf{3146} \\
               arc\_distance &    2796 &          2792 &          3084 &    2791 &  \textbf{103} \\
                        conv & 3260079 &             0 & \textbf{3284} & 3268298 &          3420 \\
                create\_grid &    5231 & \textbf{5044} &             0 &    5240 &          5587 \\
                    cronbach &    1905 &          2016 &             0 &    1909 & \textbf{1890} \\
                   diffusion &   42998 &         45030 & \textbf{8843} &   43238 &         21704 \\
                      evolve &    8236 &             0 &             0 &    8319 & \textbf{6242} \\
                        fdtd & 1940884 &       1498849 &             0 & 2007839 & \textbf{2294} \\
                         fft &   27120 &             0 &             0 &   27009 & \textbf{2151} \\
                    grouping &    3739 &             0 &             0 &    3740 & \textbf{1747} \\
                     growcut & 2112332 &         11617 & \textbf{5485} & 2141571 &         10338 \\
                      harris &    7173 &          9116 & \textbf{4240} &    7322 &          4889 \\
                     hyantes &  288852 &             0 & \textbf{2834} &  289074 &          3522 \\
                       julia & 1744357 &          5168 &  \textbf{109} & 1771329 &          4255 \\
                      l2norm &    5966 &          5948 &          9210 &    6559 &  \textbf{551} \\
               local\_maxima &  132237 &             0 &             0 &  132047 & \textbf{8561} \\
                      lstsqr &    9254 &          7528 &             0 &    8992 & \textbf{1414} \\
                      mandel &  951612 & \textbf{8175} &             0 &  951687 &         10341 \\
               multiple\_sum &    5477 &          5813 &          9805 &    5475 & \textbf{3503} \\
                    pairwise & 3362150 &         10764 &          6199 & 3347574 & \textbf{6015} \\
              periodic\_dist &    2559 &          2675 &             0 &    2562 & \textbf{2292} \\
                   repeating &    2808 &          2836 &             0 &    2795 &  \textbf{810} \\
             reverse\_cumsum &    4583 &          4828 &             0 &    4583 & \textbf{2379} \\
                       rosen &   15382 &         14309 &          2763 &   16065 &  \textbf{939} \\
                   slowparts &    8302 &             0 & \textbf{1610} &    8241 &          1927 \\
                   smoothing &  834057 &          8478 &          9771 &  819827 & \textbf{8254} \\
             specialconvolve &   12537 &         11978 &          6039 &   12570 & \textbf{5572} \\
                vibr\_energy &    5277 &          5275 &          5334 &    5416 &  \textbf{146} \\
                        wave &   72394 &         67590 &             0 &   72300 & \textbf{5186} \\
                       wdist &  108572 &        119211 &          4197 &  108283 & \textbf{4010} \\
\hline
\end{tabular}
}
\label{tbl:overview}
\caption{Average execution times for all kernels of the numpy-benchamrks on Intel8 with OpenMP (8 threads) and SIMD extension.}
\end{table*}

Figure~\ref{fig:arc_distance} and \ref{fig:arc_distance_intel8} are typicals
example where we can make intensive
use of the techniques described in this paper. It shows speedup compare to one
thread execution for the arc\_distance benchmark.This kernel performs intensive
points to points computation and trigonometrics use. We can see that OpenMP
improvement is scalable up to 20 threads with a raw array of 10,000,000 double
elements as input.
